---
title: "Tutorial on Multiple Regression"
author: "Devarshi Pancholi"
date: "7/29/2019"
output: pdf_document
---
## R Markdown

**Task:** The purpose of this analysis/tutorial is to use multiple regression to accurately forecast cost to advertize in a magazine based on various attributes in our AdCost dataset.

The Steps we will take are:

1) Load the dataset in RStudio and have a look at the data.

2) Look at the scatterplot based on the dataset.

3) Check the correlation between variables.

4) Build the multiple regression model.

5) Plot the original data and the regression line.

6) Plot the standardized residuals vs. fitted values.

**Part 1: Load the libraries and dataset in RStudio.**

```{r message= FALSE}
#loading the libraries we will use for this exercise
library(readr)
library(ggplot2)

#loading the dataset in RStudio
AdCost<-read_csv(file= "/Users/devarshipancholi/Desktop/AdCost.csv")
```

Now lets have a look at our dataset

```{r}

#printing the data to the pdf file
print(AdCost)

```

**Part 2: Look at the scatterplot.**

To plot the regression line  and scatterplot, I have used the library ggplot which we loaded in the beginning:

```{r}

# command for loading the plot and assigning the axis + plotting the points on graph in blue
# y-axis denotes our dependent variable while x-axis denotes all independent variables combined

ggplot(data= AdCost, aes(x= audience+male+income, y= pagecost)) + geom_point(color= 'blue')

```

**Part 3: Checking the co-relation **

```{r}

# removing the non numeric data from our analysis

all = AdCost[,2:5]

# 'all.obs' is used here as there are no missing data.
# 'pearson' method is used as our data is linear and normally distributed

cor(all, use="all.obs", method="pearson")

```

**Part 4:Build the multiple regression model.**

```{r}

# multiple regression model stored in the variable mamed "linearRegModel"

MultipleRegModel<- lm(pagecost ~ audience+male+income, data= AdCost)
print(MultipleRegModel)

```

Next, we get the summary for our regression model. This function allows us to observe a number of values like R-Squared, t-values and p-values for our independent varialbes.

```{r}

#getting the summary
summary(MultipleRegModel)

```

Here's how you can obtain the anova output if needed:

```{r}

anova(MultipleRegModel)

```

***Part 5: Plot the original data and the linear regression line.***

We will again use the library ggplot2 to add the regression line
```{r warning= FALSE}

# assigning the dataset
data(AdCost)

# deciding on X and Y axis + plotting the points on graph in blue
p1 = ggplot( data= AdCost,aes( x= audience+male+income,y= pagecost)) + geom_point( color= 'blue')

# plotting the regression line through the points
p1 + geom_smooth( method= 'lm', se= F, col= "red")


```

***Part 6: Plot the standardized residuals vs. fitted values.***

```{r}

# obtaining standard residuals
MultipleRegModel.StdRes <- rstandard(MultipleRegModel)

# obtaining fitted values
MultipleRegModel.Fit <- fitted.values(MultipleRegModel)

# deciding on X and Y axis + plotting the points on graph in blue
p3=ggplot(data=AdCost,aes(x=MultipleRegModel.Fit,y=MultipleRegModel.StdRes))+geom_point(color='blue')

# plotting the best fitting line through the points in red 
p3 + geom_smooth( method= 'lm', se= F, col= "red")

```

